Temporal Distinctiveness in Task Switching: Assessing the Mixture-Distribution Assumption

### 2015-11-03 2015/Temporal Distinctiveness & Mixture Distributions/Manuscript Files/main.tex
updated manuscript file

%%%--------------------------------------------------------------------------------------------
\section{Behavioural Data}
Describe the gist of the method, and provide a plot of the pertinent data
%%%--------------------------------------------------------------------------------------------

@@

\subsubsection{Episodic Retrieval}
The main processing stages in the model are shown in Figure \ref{fig:retrievalOverview}. The model assumes that, when presented with a task cue on a task repetition trial, the cognitive system attempts to retrieve the most recent episodic trace of this task (which was from trial n--1). The success of this retrieval attempt is influenced by the temporal distinctiveness of the episodic trace (at n--1) from a distracting episodic trace from the task two trials ago (at n--2).

\iftoggle{jou}{
\begin{figure}
\begin{center}
\includegraphics[width = 0.5 \textwidth]{Images/retrievalOverview.pdf}
\caption{Overview of the retrieval processes in the model.}
\label{fig:retrievalOverview}
\end{center}
\end{figure}
}{
\begin{figure}
\begin{center}
\includegraphics[width = \textwidth]{Images/retrievalOverview.pdf}
\caption{Overview of the retrieval processes in the model.}
\label{fig:retrievalOverview}
\end{center}
\end{figure}
}

@@

Figure \ref{fig:lbaAccumulation} shows how the LBA is applied in the current context. (Note that only the correct accumulators are shown to avoid clutter.) The model only ever uses one of two accumulation processes: If retrieval is successful, the model samples the current RT from a ``successful'', ``fast'' accumulation process with a higher drift rate, $v_{Fast}$; if retrieval fails, the current RT is sampled from an ``unsuccessful'', ``slow'' accumulation process with a lower drift rate, $v_{Slow}$.

\iftoggle{jou}{
\begin{figure}
\begin{center}
\includegraphics[width = 0.5 \textwidth]{Images/lbaAccumulation.pdf}
\caption{Overview of the Linear Ballistic Accumulation Process for successful and unsuccessful retrieval.}
\label{fig:lbaAccumulation}
\end{center}
\end{figure}
}{
\begin{figure}
\begin{center}
\includegraphics[width = 0.5 \textwidth]{Images/lbaAccumulation.pdf}
\caption{Overview of the Linear Ballistic Accumulation Process for successful and unsuccessful retrieval.}
\label{fig:lbaAccumulation}
\end{center}
\end{figure}
}

@@

>>>>

\begin{figure} 
\begin{center}
\includegraphics[width = 0.5 \textwidth]{Images/tdAccount.pdf}
\caption{Schematic overview of the temporal distinctiveness account of response--cue interval effects in task switching. See text for details.}
\label{fig:tdAccount}
\end{center}
\end{figure}

%%%--------------------------------------------------------------------------------------------
\section{Behavioural Data}
Describe the gist of the method, and provide a plot of the pertinent data.

Consider a portion of data reported by Grange (in revision), which can be seen in Figure \ref{fig:grangeData} (see Appendix A for pertinent aspects of the method and statistical analysis). Largely replicating earlier work \citep{Horoufchin2011, Horoufchin2011a}, the reduction in switch cost at extended RCIs was significantly larger when the RCI was different from the previous trial (right panel of Figure \ref{fig:grangeData}) than when it was the same (left panel of Figure \ref{fig:grangeData}), as reflected by the significant three-way interaction (see Appendix A for the ANOVA summary table). Thus, this data is in accordance with the temporal distinctiveness account, and cannot be easily explained by a decay account.

\iftoggle{jou}{
\begin{figure}
\begin{center}
\includegraphics[width = 0.5\textwidth]{Images/grangeData.pdf}
\caption{Data from Grange (in preparation) showing mean response time in milliseconds (ms) for task repetition and switch trials as a function of the current response--cue interval (x-axis) and whether the RCI is the same or different from the previous trial. Error bars denote  +/- 1 standard error around the mean.}
\label{fig:grangeData}
\end{center}
\end{figure}
}{
\begin{figure}
\begin{center}
\includegraphics[width = \textwidth]{Images/grangeData.pdf}
\caption{Data from Grange (in preparation) showing mean response time in milliseconds (ms) for task repetition and switch trials as a function of the current response--cue interval (x-axis) and whether the RCI is the same or different from the previous trial. Error bars denote  +/- 1 standard error around the mean.}
\label{fig:grangeData}
\end{center}
\end{figure}
}

% Table generated by Excel2LaTeX from sheet 'Sheet1'
\begin{table}[htbp]
  \centering
  \caption{ANOVA summary table for response time data from Grange (in preparation).}
    \begin{tabular}{rrrrr}
    \toprule
    Source & df    & \emph{F}     & \emph{p}     & $\eta_{g}^{2}$ \\
    \midrule
    Sequence (S) & 1 , 24 & 118.94 & $<$.001 & 0.469 \\
    RCI (R) & 1 , 24 & 12.61 & 0.002 & 0.022 \\
    RCI-Change (RC) & 1 , 24 & 15.68 & $<$.001 & 0.015 \\
    S * R & 1 , 24 & 32.03 & $<$.001 & 0.024 \\
    S * RC & 1 , 24 & 4.95  & 0.036 & 0.002 \\
    R * RC & 1 , 24 & 12.26 & 0.002 & 0.021 \\
    S * R * RC & 1 , 24 & 18.3  & $<$.001 & 0.008 \\
    \bottomrule
    \end{tabular}%
  \label{tab:grangeData}%
\end{table}%

@@

\subsubsection{Episodic Retrieval}
The main processing stages in the model are shown in Figure \ref{fig:modelOverview}. The model assumes that, when presented with a task cue on a task repetition trial, the cognitive system attempts to retrieve the most recent episodic trace of this task (which was from trial n--1). The success of this retrieval attempt is influenced by the temporal distinctiveness of the episodic trace (at n--1) from a distracting episodic trace from the task two trials ago (at n--2).

\iftoggle{jou}{
\begin{figure}
\begin{center}
\includegraphics[width = 0.5 \textwidth]{Images/modelOverview.pdf}
\caption{Overview of the retrieval processes in the model.}
\label{fig:modelOverview}
\end{center}
\end{figure}
}{
\begin{figure}
\begin{center}
\includegraphics[width = \textwidth]{Images/modelOverview.pdf}
\caption{Overview of the retrieval processes in the model.}
\label{fig:modelOverview}
\end{center}
\end{figure}
}

@@

The Upper portion of Figure \ref{fig:modelOverview} shows how the LBA is applied in the current context. (Note that only the correct accumulators are shown to avoid clutter.) The model only ever uses one of two accumulation processes: If retrieval is successful, the model samples the current RT from a ``successful'', ``fast'' accumulation process with a higher drift rate, $v_{Fast}$; if retrieval fails, the current RT is sampled from an ``unsuccessful'', ``slow'' accumulation process with a lower drift rate, $v_{Slow}$.

@@

%%%--------------------------------------------------------------------------------------------
\appendix
\section{Method and Results of Grange's (in preparation) Behavioural Experiment}

% Table generated by Excel2LaTeX from sheet 'Sheet1'
\begin{table}[htbp]
  \centering
  \caption{ANOVA summary table for response time data from Grange (in preparation).}
    \begin{tabular}{rrrrr}
    \toprule
    Source & df    & \emph{F}     & \emph{p}     & $\eta_{g}^{2}$ \\
    \midrule
    Sequence (S) & 1 , 24 & 118.94 & $<$.001 & 0.469 \\
    RCI (R) & 1 , 24 & 12.61 & 0.002 & 0.022 \\
    RCI-Change (RC) & 1 , 24 & 15.68 & $<$.001 & 0.015 \\
    S * R & 1 , 24 & 32.03 & $<$.001 & 0.024 \\
    S * RC & 1 , 24 & 4.95  & 0.036 & 0.002 \\
    R * RC & 1 , 24 & 12.26 & 0.002 & 0.021 \\
    S * R * RC & 1 , 24 & 18.3  & $<$.001 & 0.008 \\
    \bottomrule
    \end{tabular}%
  \label{tab:grangeData}%
\end{table}%
